\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\usepackage{hyperref}

\begin{document}

  \section*{What is Taraya?}

  \textbf{Taraya} is the \textit{ascendant flow} of civilization's next substrate --- \\
  a \textbf{city-scale sovereign infrastructure platform} for AI, biosimulation, and advanced compute. \\
  It’s not just a fab or datacenter — it’s where the \textbf{next 100 years of intelligence begins}.

  \vspace{1em}

  \subsection*{Tagline}
  \begin{quote}
    \textbf{Taraya} \\
    \textit{Ascendant Flow.} \\
    \textit{The next 100 years of compute for intelligence.}
  \end{quote}

  \vspace{1em}

  \section*{Mythos: Where the Future Blooms}

  The name \textbf{Taraya} draws from \textit{tārā} — the celestial guide — and \textit{raya} — flow, lineage, path. \\
  It is both \textbf{a wave and a crown}, a place where \textbf{sovereign technology is born}, not licensed. \\
  A spiritual descendant of the civilizations that gave us \textbf{zero, algebra, and logic}, \\
  Taraya is where that \textbf{mathematical lineage incarnates as physical infrastructure} — \\
  trusted, post-TSMC, and globally independent.

  \begin{itemize}
    \item It is \textit{not the cloud}.
    \item It is \textit{not a hyperscaler’s lease}.
    \item It is \textbf{a compute throne} — and \textbf{you can host it}.
  \end{itemize}

  \vspace{1em}

  \section*{City-Scale Physical Reality}

  Taraya is a \textbf{civilization-scale zone} with tightly integrated verticals, structured like a living system:

  \subsection*{Core Zones (Cookie-Cutter, Replicable)}
  \begin{itemize}
    \item \textbf{Twin Fab Cluster} – 3nm + 7nm copy-exact fabrication
    \item \textbf{Packaging \& Assembly Village} – High mix, sovereign test + bond
    \item \textbf{Datacenter Village} – Sovereign LLM/AI deployment, defense-ready
    \item \textbf{Design Village} – IP incubation, chiplet orchestration, AI stack R\&D
    \item \textbf{Biosimulation Village} – Drug dev, life sciences, virtual labs
    \item \textbf{Vendor Village} – Co-located suppliers: optics, vacuum, substrates, chemicals
    \item \textbf{Logistics + Bonded Zone} – Tools, customs-free corridor, critical spares
    \item \textbf{Power + Cooling Zone} – Gas, solar annex, seawater desalination
    \item \textbf{Living Infrastructure} – 15-minute city: family housing, nightlife, schooling
  \end{itemize}

  \vspace{1em}

  \section*{Crown Jewel-Level Security \& Sovereignty}

  Taraya is not built on sand — it is \textbf{rooted in geopolitical foresight} and \textbf{protected like a kingdom}:

  \begin{itemize}
    \item \textbf{SPZA Charter} – Full sovereign policy stack, bonded lanes, tax code
    \item \textbf{NOC + SOC Core} – EMP-shielded, biometric command center
    \item \textbf{No-Fly Perimeter} – Modeled after HIA + UAE CICPA zones
    \item \textbf{Rapid Access Grid} – Helipads, tunnels, drone rails
    \item \textbf{Cyber-physical trust architecture} – BIOS to bootchain to container
    \item \textbf{Paramilitary perimeter force} – On-site, Qatari/Lekhwiya-class
    \item \textbf{Decentralized federation} – India, Qatar, UAE, KSA: competing and cooperating
  \end{itemize}

  \vspace{1em}

  \section*{Summary Line (G20-grade)}

  \begin{quote}
    \textbf{Taraya is where sovereign nations stop renting the future — and start hosting it.} \\
    It is the \textbf{trusted leading source} of AI, biosimulation, and silicon — \\
    built on the ground, defended by design, and replicated to change the world.
  \end{quote}

\end{document}
