
\documentclass[12pt]{article}
\usepackage[T1]{fontenc}
\usepackage[margin=0.5in]{geometry}
\usepackage{microtype}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{lmodern}
\usepackage{parskip}
\usepackage{graphicx}
\usepackage{hyperref}
\pagestyle{empty}

\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}

\begin{document}
\begin{center}
    {\huge \textbf{Taraya}} {\Large :: Ascendant Flow.}\\[0.5em]
    {\Large The heart of the digital sovereign for the next 100 years and beyond.}\\[2em]
\end{center}

\begin{spacing}{1.15}

\noindent
\textbf{Taraya is a planned, sovereign, civilization-scale compute city — designed to secure the future of national intelligence, bio-research, and advanced manufacturing for the next century.}

\vspace{1em}
\noindent
Built as a response to rising geopolitical risk, Taraya begins as \textbf{Black Swan Insurance} — a sovereign fallback for AI and biosimulation workloads — but rapidly expands into a fully self-contained, vertically integrated ecosystem for global technology leadership.

\section*{Strategic Vision (100-Year Plan)}
\begin{itemize}
  \item Fully sovereign, end-to-end compute and manufacturing stack
  \item Engineered resilience: no dependency on unstable or adversarial regions
  \item Entire lifecycle covered:
      \begin{center}
        raw materials|power generation|cooling|process chemicals|design| \\
        silicon foundry|datacenter|assembly|global shipment
      \end{center}
  \item Backbone for AI, biotech, advanced sensing, and sovereign cloud
\end{itemize}

\section*{The City Itself}
\begin{itemize}
  \item 15-minute live/work/play design — families, shopping, schools, not just facilities
  \item Twin fabs (advanced + mature nodes), packaging, datacenter assembly, device manufacturing
  \item Dedicated zones for upstream mining inputs and downstream export integration
  \item Near a major air logistics hub for secure, high-speed global reach
  \item Attractive living environment: education, culture, resilience, and green infrastructure
\end{itemize}

\section*{Why India?}
\begin{itemize}
  \item Strategic geography: east-west redundancy and global neutrality
  \item Rising technology and manufacturing power
  \item Strong governance and pro-sovereignty leadership
  \item Existing human capital in biotech, compute, and advanced engineering
\end{itemize}

\vspace{1em}
\noindent
\textbf{Taraya is not just a backup plan. It's the new primary.}  
A digital continent for the future of civilization — founded now, for the next 100 years and beyond.

\end{spacing}
\end{document}
