\documentclass[12pt]{article}
\usepackage[T1]{fontenc}
\usepackage[margin=0.5in]{geometry}
\usepackage{microtype}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{lmodern}
\usepackage{parskip}
\usepackage{graphicx}
\usepackage{hyperref}
\pagestyle{empty}

\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}
\titlespacing*{\section}{0pt}{0.75em}{0.5em}
\setlength{\parskip}{0.5em}
\usepackage{enumitem}
\setlist[itemize]{itemsep=0.1em, topsep=0.25em, parsep=0em, partopsep=0em}

\begin{document}
    \begin{center}
    {\huge \textbf{Taraya}} {\Large :: Ascendant Flow.}\\[0.25em]
    {\large The heart of the digital sovereign for the next 100 years and beyond.}\\[1em]
    \end{center}

    \begin{spacing}{1.08}

        \noindent
        \textbf{Taraya is a planned, sovereign, civilization-scale compute city \textemdash{} designed to secure the future of national intelligence, bio-research, and advanced manufacturing for the next century.}

        \noindent
        Taraya shifts the foundation of digital civilization from fragile dependencies to sovereign strength, continuity, and trust.  First envisioned as a sovereign alternative for AI and biosimulation workloads, Taraya rapidly expands into a fully self-contained, vertically integrated ecosystem for global technology leadership.

        \section*{Strategic Vision (100-Year Plan)}
        \begin{itemize}
            \item Fully sovereign, end-to-end compute and manufacturing stack
            \item Engineered resilience: no dependency on unstable or adversarial regions
            \item Entire lifecycle covered:
            \begin{center}
                raw materials|power generation|cooling|process chemicals|design| \\
                silicon foundry|datacenter|assembly|global shipment
            \end{center}
            \item Backbone for AI, biotech, advanced sensing, and sovereign cloud
            \item Anchors a multipolar digital order — reducing the world's reliance on fragile, centralized compute ecosystems
        \end{itemize}

        \section*{The City Itself}
        \begin{itemize}
            \item 15-minute live/work/play design \textemdash{} families, shopping, schools, not just facilities
            \item Twin fabs (advanced + mature nodes), packaging, datacenter assembly, device manufacturing
            \item Dedicated zones for upstream mining inputs and downstream export integration
            \item Near a major air logistics hub for secure, high-speed global reach
            \item Attractive living environment: education, culture, resilience, and green infrastructure
            \item \textit{“Designed to cultivate next-generation Emirati leadership in science, security, and sovereignty.”}
        \end{itemize}

        \section*{Why the UAE?}
        \begin{itemize}
            \item Global logistics and digital infrastructure leadership — from ports to space
            \item Mubadala delivers state-scale execution with venture-grade velocity
            \item Neutral capital, trusted across East, West, and the Global South
            \item Taraya extends the UAE’s sovereign operating system for AI, health, and energy in alignment with Vision 2071.
            \item Directly aligned with national goals for economic diversification and technological permanence
            \item The UAE is uniquely positioned to offer trusted, durable digital infrastructure for global civilization
            \item Requires only a sovereign blessing for alignment of ministries to proceed: execution channels are already in motion
        \end{itemize}

        \noindent
        \textbf{Taraya is the UAE’s sovereign anchor for the post-hydrocarbon age.} \\
        A civilization-scale platform for technological permanence, neutral reach, and global influence — founded now, for the next 100 years and beyond.


        \vspace{1.5em}
        \begin{flushright}
            {\footnotesize Taraya concept briefing. Strategic correspondence: \texttt{contact@taraya.tech}}
        \end{flushright}
    \end{spacing}
\end{document}
